Hemispheric Lateralization in ICH

### 2023-06-28 code/dataAnalysis/02analysis.qmd
euroVAS regression

library(tidyverse)
# library(gt) # Fancy tables
library(tableone)
library(data.table)
library(haven) # Importing SAS Files
library(janitor)
library(lubridate)
library(readxl)
library(Hmisc)
# library(qreport)
library(stringr)
library(qs)
library(glue)
library(scales) # Nicer labeling functions
library(ggmosaic) # Mosaic plots with ggplot
library(ggplot2)
library(ggpattern) # Pattern fills in ggplot
library(patchwork) # Combine plots nicely
library(systemfonts) ## use custom fonts (need to be installed on your OS)
library(scico) ## scico color palettes(http://www.fabiocrameri.ch/colourmaps.php) in R
library(ggtext) ## add improved text rendering to ggplot2
library(ggforce) ## add missing functionality to ggplot2
library(ggdist) ## add uncertainity visualizations to ggplot2
library(viridis)
library(dagitty)
library(rlang)
# library(ggokabeito)

@@

**Add Deaths to ATACH data!**

@@

>>>>

library(tidyverse)
# library(gt) # Fancy tables
library(tableone)
library(data.table)
library(haven) # Importing SAS Files
library(janitor)
library(lubridate)
library(readxl)
library(Hmisc)
# library(qreport)
library(stringr)
library(qs)
library(glue)
library(scales) # Nicer labeling functions
library(ggmosaic) # Mosaic plots with ggplot
library(ggplot2)
library(ggpattern) # Pattern fills in ggplot
library(patchwork) # Combine plots nicely
library(systemfonts) ## use custom fonts (need to be installed on your OS)
library(scico) ## scico color palettes(http://www.fabiocrameri.ch/colourmaps.php) in R
library(ggtext) ## add improved text rendering to ggplot2
library(ggforce) ## add missing functionality to ggplot2
library(ggdist) ## add uncertainity visualizations to ggplot2
library(viridis)
library(dagitty)
library(rlang)
library(bayesrules)
library(rstanarm)
library(bayesplot)
library(broom.mixed)
library(tidybayes)
# library(ggokabeito)

@@

@@

### EuroQOL Visual Analog Scale

Let's define functional outcome as EuroQOL VAS, an outcome measure from 0-100.

```{r}
d |>
  ggplot(aes(x = euroVAS90, fill = ichLaterality)) +
  geom_density(alpha = 0.5)

eurovas90Model <- stan_glm(
  euroVAS90 ~ ichLaterality,
  data = d,
  family = gaussian,
  iter = 5000,
  warmup = 2000,
  thin = 10,
  cores = 4,
  seed = 1234
)

summary(eurovas90Model)

tidy(eurovas90Model,
  effects = c("fixed", "aux"),
  conf.int = TRUE, conf.level = 0.89
) |>
  select(-std.error)

# MCMC diagnostics

mcmc_trace(eurovas90Model, size = 0.1)
mcmc_dens_overlay(eurovas90Model)
mcmc_acf(eurovas90Model)

## Posterior predictive checks

pp_check(eurovas90Model)

## Posterior models

head(as.data.frame(eurovas90Model))
